Pituitary

### 2020-08-06 analysis/boneyard.Rmd
not sure i like it but same 3 figs for hyp pit gon

## other DEG stuff
hypsex <- read_csv("../results/DEseq2/sex/hypothalamus_female_male_DEGs.csv")
pitsex <- read_csv("../results/DEseq2/sex/pituitary_female_male_DEGs.csv")
gonsex <- read_csv("../results/DEseq2/sex/gonad_female_male_DEGs.csv")

@@

b2 <- sexbarplots(hyppit, 0, 8100) + labs(subtitle = " ", y = "DEGs w/ + LFC") +
  theme(axis.text.y = element_blank(), axis.ticks = element_blank()) +
  scale_x_discrete(labels=c("hypothalamus" = "hyp", "pituitary" = "pit" ))
b3 <- sexbarplots(hypgon, 0, 8100) + labs(subtitle = " " ) +
  theme(axis.text.y = element_blank(), axis.line.y = element_blank(), 
        axis.ticks = element_blank(), axis.title.y = element_blank()) +
    scale_x_discrete(labels=c("hypothalamus" = "hyp",  "gonad" = "gon"))
b4 <- sexbarplots(pitgon, 0, 8100) + labs(subtitle = " " ) +
  theme(axis.text.y = element_blank(), axis.line.y = element_blank(),  
        axis.ticks = element_blank(), axis.title.y = element_blank()) +
    scale_x_discrete(labels=c(  "pituitary" = "pit", "gonad" = "gon"))
c1 <- plottsneelipse(chartsne, chartsne$sex, allcolors)   + labs(y = "tSNE 2 ", subtitle = " ")    
c2 <- sexbarplots(hypsex, 0, 8100) + labs(y = "DEGs w/ + LFC", subtitle = "hypothalamus" ) +
  theme(axis.text.y = element_blank(), axis.ticks = element_blank())
c3 <- sexbarplots(pitsex, 0, 8100) + labs(subtitle = "pituitary" ) + 
  theme(axis.text.y = element_blank(), axis.line.y = element_blank(),  
        axis.ticks = element_blank(), axis.title.y = element_blank())
c4 <- sexbarplots(gonsex, 0, 8100) + labs(subtitle = "gonads" ) +
  theme(axis.text.y = element_blank(), axis.line.y = element_blank(),  
        axis.ticks = element_blank(), axis.title.y = element_blank())
bc <- plot_grid(b1,b2,b3,b4, c1,c2,c3,c4, nrow = 1, rel_widths = c(1.5,1.1,0.9,0.9,1.5,1.1,0.9,0.9),
                labels = c("A", "", "", "", "B"), label_size = 8)
```

@@

s1a <- makebargraphsuppl(DEGcontrol, "hypothalamus","DEGs w/ + LFC", 0, 5000) + 
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) + 
  labs(subtitle = "hypothalamus") 
s1c <- makebargraphsuppl(DEGcontrol, "pituitary","DEGs w/ + LFC", 0, 5000)  +  
  theme(axis.text.x = element_blank(), 
        axis.title.x = element_blank(), 
        strip.text.x = element_blank())    + 
  labs(subtitle = "pituitary") 
s1e <- makebargraphsuppl(DEGcontrol, "gonad","DEGs w/ + LFC", 0, 5000) +  
  theme(strip.text.x = element_blank()) +
  scale_x_discrete(labels = comparisonlabelscontrol) +
  labs(subtitle = "gonads")

s1b <- makebargraphsuppl(DEGbldg, "hypothalamus", NULL, 0, 1000) + 
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())  
s1d <- makebargraphsuppl(DEGbldg, "pituitary",NULL, 0, 1000)  +  
  theme(axis.text.x = element_blank(), 
        axis.title.x = element_blank(), 
        strip.text.x = element_blank())   
s1f <- makebargraphsuppl(DEGbldg, "gonad",NULL, 0, 1000) +  
  theme(strip.text.x = element_blank()) +
  scale_x_discrete(labels = comparisonlabelsbldg)

@@

# for volcano plots
hyphatch <- DEGchar %>% filter(tissue == "hypothalamus", comparison == "hatch_n5") 
pitinc <- DEGchar %>% filter(tissue == "pituitary", comparison == "inc.d9_inc.d17") 
goninc <- DEGchar %>% filter(tissue == "gonad", comparison == "lay_inc.d3")

>>>>

## other DEG stuff

pitsex <- read_csv("../results/DEseq2/sex/pituitary_female_male_DEGs.csv")
gonsex <- read_csv("../results/DEseq2/sex/gonad_female_male_DEGs.csv")

@@

b2 <- sexbarplots(hyppit, 0, 8100) + labs(subtitle = " ", y = "DEGs w/ + LFC") +
  theme(axis.text.y = element_blank(), axis.ticks = element_blank()) +
  scale_x_discrete(labels=c("hypothalamus" = "hyp", "pituitary" = "pit" ))
b3 <- sexbarplots(hypgon, 0, 8100) + labs(subtitle = " " ) +
  theme(axis.text.y = element_blank(), axis.line.y = element_blank(), 
        axis.ticks = element_blank(), axis.title.y = element_blank()) +
    scale_x_discrete(labels=c("hypothalamus" = "hyp",  "gonad" = "gon"))
b4 <- sexbarplots(pitgon, 0, 8100) + labs(subtitle = " " ) +
  theme(axis.text.y = element_blank(), axis.line.y = element_blank(),  
        axis.ticks = element_blank(), axis.title.y = element_blank()) +
    scale_x_discrete(labels=c(  "pituitary" = "pit", "gonad" = "gon"))

c3 <- sexbarplots(pitsex, 0, 8100) + labs(subtitle = "pituitary" ) + 
  theme(axis.text.y = element_blank(), axis.line.y = element_blank(),  
        axis.ticks = element_blank(), axis.title.y = element_blank())
c4 <- sexbarplots(gonsex, 0, 8100) + labs(subtitle = "gonads" ) +
  theme(axis.text.y = element_blank(), axis.line.y = element_blank(),  
        axis.ticks = element_blank(), axis.title.y = element_blank())
bc <- plot_grid(b1,b2,b3,b4, c1,c2,c3,c4, nrow = 1, rel_widths = c(1.5,1.1,0.9,0.9,1.5,1.1,0.9,0.9),
                labels = c("A", "", "", "", "B"), label_size = 8)
```

@@

s1c <- makebargraphsuppl(DEGcontrol, "pituitary","DEGs w/ + LFC", 0, 5000)  +  
  theme(axis.text.x = element_blank(), 
        axis.title.x = element_blank(), 
        strip.text.x = element_blank())    + 
  labs(subtitle = "pituitary") 
s1e <- makebargraphsuppl(DEGcontrol, "gonad","DEGs w/ + LFC", 0, 5000) +  
  theme(strip.text.x = element_blank()) +
  scale_x_discrete(labels = comparisonlabelscontrol) +
  labs(subtitle = "gonads")

s1d <- makebargraphsuppl(DEGbldg, "pituitary",NULL, 0, 1000)  +  
  theme(axis.text.x = element_blank(), 
        axis.title.x = element_blank(), 
        strip.text.x = element_blank())   
s1f <- makebargraphsuppl(DEGbldg, "gonad",NULL, 0, 1000) +  
  theme(strip.text.x = element_blank()) +
  scale_x_discrete(labels = comparisonlabelsbldg)

@@

# for volcano plots

pitinc <- DEGchar %>% filter(tissue == "pituitary", comparison == "inc.d9_inc.d17") 
goninc <- DEGchar %>% filter(tissue == "gonad", comparison == "lay_inc.d3")

### 2020-08-06 analysis/figure-1.Rmd
now with session info
not sure i like it but same 3 figs for hyp pit gon

```{r setup, include=FALSE}
library(tidyverse)
library(cowplot)
library(Rtsne)

@@

png("../figures/fig1-1.png", width = 7, height = 4.5, 
    units = 'in', res = 300)
plot(fig1) # Make plot
dev.off()
```

>>>>

```{r setup, include=T}
library(tidyverse)
library(cowplot)
library(Rtsne)

@@

png("../figures/fig1-1.png", width = 7, height = 4.5, 
    units = 'in', res = 300)
plot(fig1) # Make plot
dev.off()

sessionInfo()
```

### 2020-08-06 analysis/hypothalamus.Rmd
not sure i like it but same 3 figs for hyp pit gon

---
title: "Gonad"
output: md_document
---

# Gonad

@@

```{r suppltables}
allDEG <- read_csv("../results/03_allDEG.csv") %>%
  mutate(tissue = factor(tissue, levels = tissuelevel),
         direction = factor(direction, levels = alllevels),
         label = gsub("_","\nvs. ", comparison)) %>%
  filter(tissue == "gonad")
allDEG

@@

candidatevsd <- read_csv("../results/03_candidatevsd.csv") %>% 
  select(-X1) %>%
  filter(treatment %in% charlevels) %>%
  mutate(treatment = factor(treatment, levels = charlevels)) %>%
  drop_na() %>%
    mutate(external = fct_collapse(treatment, 
                                   "none" = c("control", "bldg"),
                                   "eggs" = c("lay" , "inc.d3", 
                                              "inc.d9", "inc.d17"),
                                   "chicks" = c("hatch", "n5", "n9")))
```

```{r gonad, fig.width=7, fig.height=7}

a <- plot.volcano("gonad", sexlevels,  "control_bldg") + 
  facet_wrap(~sex) +  labs(title = "Gonad") 
b <- makebargraph(DEGcontrol, "gonad","DEGs w/ + LFC", 0, 4200, comparisonlabelscontrol) 
  labs(title = " ")

c <- makebargraph(DEGbldg, "gonad", "DEGs w/ + LFC", 0, 2200, comparisonlabelsbldg) 
d <- makebargraph(DEGchar, "gonad","DEGs w/ + LFC", 0, 1500, comparisonlabelscharnobldg)

e <- candidateboxplot("gonad",  c("ESR1"), sexlevels)
f <- candidateboxplot("gonad",  c("PGR"), sexlevels)

@@

goncharfig <- plot_grid(ab,cd,ef, ncol = 1)
goncharfig
```

@@

```{r write}
pdf(file="../figures/pitcharfig.pdf", width=7, height=7)
plot(goncharfig)
dev.off()

png("../figures/pitcharfig.png", width = 7, height = 7, 
    units = 'in', res = 300)
plot(goncharfig) # Make plot
dev.off()

>>>>

---
title: "Hypothalamus"
output: md_document
---

# Hypothalamus

@@

```{r suppltables}
allDEG <- read_csv("../results/03_allDEG.csv") %>%
  mutate(tissue = factor(tissue, levels = tissuelevel),
         direction = factor(direction, levels = alllevels),
         label = gsub("_","\nvs. ", comparison)) %>%
  filter(tissue == "hypothalamus")
allDEG

@@

candidatevsd <- read_csv("../results/03_candidatevsd.csv") %>% 
  select(-X1) %>%
  filter(treatment %in% charlevels) %>%
  mutate(treatment = factor(treatment, levels = charlevels)) %>%
  drop_na() %>%
    mutate(external = fct_collapse(treatment, 
                                   "none" = c("control", "bldg"),
                                   "eggs" = c("lay" , "inc.d3", 
                                              "inc.d9", "inc.d17"),
                                   "chicks" = c("hatch", "n5", "n9")))
head(candidatevsd)
```

```{r hypothalamus, fig.width=7, fig.height=7}

a <- plot.volcano("hypothalamus", sexlevels,  "control_bldg") + 
  facet_wrap(~sex) +  labs(title = "Hypothalamus") 
b <- makebargraph(DEGcontrol, "hypothalamus","DEGs w/ + LFC", 0, 4800, comparisonlabelscontrol) 
  labs(title = " ")

c <- makebargraph(DEGbldg, "hypothalamus", "DEGs w/ + LFC", 0, 480, comparisonlabelsbldg) 
d <- makebargraph(DEGchar, "hypothalamus","DEGs w/ + LFC", 0, 1700, comparisonlabelscharnobldg)

e <- candidateboxplot("hypothalamus",  c("DRD1"), sexlevels)
f <- candidateboxplot("hypothalamus",  c("COMT"), sexlevels)

@@

hypcharfig <- plot_grid(ab,cd,ef, ncol = 1)
hypcharfig
```

@@

```{r write}
pdf(file="../figures/hypcharfig.pdf", width=7, height=7)
plot(hypcharfig)
dev.off()

png("../figures/hypcharfig.png", width = 7, height = 7, 
    units = 'in', res = 300)
plot(hypcharfig) # Make plot
dev.off()

### 2020-08-06 analysis/pituitary.Rmd
not sure i like it but same 3 figs for hyp pit gon

---
title: "Gonad"
output: md_document
---

# Gonad

@@

```{r suppltables}
allDEG <- read_csv("../results/03_allDEG.csv") %>%
  mutate(tissue = factor(tissue, levels = tissuelevel),
         direction = factor(direction, levels = alllevels),
         label = gsub("_","\nvs. ", comparison)) %>%
  filter(tissue == "gonad")
allDEG

@@

```{r gonad, fig.width=7, fig.height=7}

a <- plot.volcano("gonad", sexlevels,  "control_bldg") + 
  facet_wrap(~sex) +  labs(title = "Gonad") 
b <- makebargraph(DEGcontrol, "gonad","DEGs w/ + LFC", 0, 4200, comparisonlabelscontrol) 
  labs(title = " ")

c <- makebargraph(DEGbldg, "gonad", "DEGs w/ + LFC", 0, 2200, comparisonlabelsbldg) 
d <- makebargraph(DEGchar, "gonad","DEGs w/ + LFC", 0, 1500, comparisonlabelscharnobldg)

e <- candidateboxplot("gonad",  c("ESR1"), sexlevels)
f <- candidateboxplot("gonad",  c("PGR"), sexlevels)

@@

goncharfig <- plot_grid(ab,cd,ef, ncol = 1)
goncharfig
```

@@

```{r write}
pdf(file="../figures/pitcharfig.pdf", width=7, height=7)
plot(goncharfig)
dev.off()

png("../figures/pitcharfig.png", width = 7, height = 7, 
    units = 'in', res = 300)
plot(goncharfig) # Make plot
dev.off()

>>>>

---
title: "Pituitary"
output: md_document
---

# Pituitary

@@

```{r suppltables}
allDEG <- read_csv("../results/03_allDEG.csv") %>%
  mutate(tissue = factor(tissue, levels = tissuelevel),
         direction = factor(direction, levels = alllevels),
         label = gsub("_","\nvs. ", comparison)) %>%
  filter(tissue == "pituitary")
allDEG

@@

```{r pituitary, fig.width=7, fig.height=7}

a <- plot.volcano("pituitary", sexlevels,  "control_bldg") + 
  facet_wrap(~sex) +  labs(title = "Pituitary") 
b <- makebargraph(DEGcontrol, "pituitary","DEGs w/ + LFC", 0, 4200, comparisonlabelscontrol) 
  labs(title = " ")

c <- makebargraph(DEGbldg, "pituitary", "DEGs w/ + LFC", 0, 2200, comparisonlabelsbldg) 
d <- makebargraph(DEGchar, "pituitary","DEGs w/ + LFC", 0, 1500, comparisonlabelscharnobldg)

e <- candidateboxplot("pituitary",  c("PRL"), sexlevels)
f <- candidateboxplot("pituitary",  c("FSHB"), sexlevels)

@@

pitcharfig <- plot_grid(ab,cd,ef, ncol = 1)
pitcharfig
```

@@

```{r write}
pdf(file="../figures/pitcharfig.pdf", width=7, height=7)
plot(pitcharfig)
dev.off()

png("../figures/pitcharfig.png", width = 7, height = 7, 
    units = 'in', res = 300)
plot(pitcharfig) # Make plot
dev.off()
